The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-04-16 src/ms.tex
add cython reference

In some cases, feature enhancements and corner-case handling were added
at the cost of performance.
Hence, \github pull requests that improve performance are welcomed, and were even the
main goal for v3.1 release. For most sub-packages, performance was
improved in the \python\ code, but for some, the most time-critical pieces were
rewritten in~C (e.g., for convolution of images, sigma-clipping, and converting
time strings to binary). Furthermore, a particular effort was made to ensure
\astropypkg\ is thread-safe, so that it can be used on supercomputing clusters.

>>>>

In some cases, feature enhancements and corner-case handling were added
at the cost of performance.
Hence, \github pull requests that improve performance are welcomed, and were
even the main goal for v3.1 release. For most sub-packages, performance was
improved in the \python\ code, but for some, the most time-critical pieces were
rewritten in~C and wrapped with \package{Cython} (\citealt{cython}; e.g., for
convolution of images, sigma-clipping, and converting time strings to binary).
Furthermore, a particular effort was made to ensure \astropypkg\ is thread-safe,
so that it can be used on supercomputing clusters.
